Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
Rough sketch for implementation of hspec-discover

>>>>

\newpage % FIXME
\subsection{hspec-discover}

As discussed in \ref{} we use a preprocessor to automatically generate
test drivers.  GHC invokes preprocessors with three arguments.

\begin{description}
    \item[{\tt src}]
        The original source file.  A preprocessor usually does not
        look at the content of this file.  It is only provided, so
        that it can be used in error messages.
    \item[{\tt cur}]
        The file that holds the input for the preprocessor.
    \item[{\tt dst}]
        A path, where the preprocessor should write it's result to.
\end{description}

\noindent A typical preprocessor reads the content of {\tt cur},
processes it, and writes the result to {\tt dst}.  If something goes
wrong, it uses {\tt src} in error messages.

\verb|hspec-discover| ignores {\tt cur} altogether.  It uses the
directory component of {\tt src}, to find all files that are in the
same directory as {\tt src}, or any subdirectories.  It than generates
a test driver from all files that end in {\tt Spec.hs}.

A fully functional implementations is available from
Hackage\footnote{http://hackage.haskell.org/package/hspec-discover},
and it will be incorporate into a future release of Hspec.
